Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-04 manuscript/cpcrw_manuscript.Rmd
Added methods re open experiment
Text and formula re flux computation

```{r, echo=FALSE}
library(dplyr)
```

@@

* joined with mass data
* flux computation
* stats

All data analysis and statistics were performed using R version 3.2.3 {R Development Core Team, 2016 #4314}.

**Data and code availability**

Note open experiment...

>>>>

```{r, echo=FALSE}
library(dplyr, warn.conflicts = FALSE)
```

@@

* joined with mass data
* flux computation

The GHG concentration measurements for each sample (i.e., each gas, core, and date/time) were used to calculate a linear rate of change (δc/δt), based on the concentration rise from a minimum (at 2-10 seconds after measurement began) to a maximum (at 10-45 seconds). Each core’s respiration flux (F) was then calculated following e.g. Steduto et al. {, 2002 #3383} as $F=\frac{\delta c}{\delta t} \frac{V}{M} \frac{P_a}{RT}$ where V is the core-specific system volume, M the core dry mass as determined at the end of the incubation, Pa atmospheric pressure (101 kPa; the incubation chambers were ~120 m a.s.l.), R the universal gas constant (8.3 x 10^-3^ m^3^ kPa mol^-1^ K^-1^) and T the chamber air temperature (K) at time of measurement. The final respiration rate was expressed as mg C kg soil^-1^ day^-1^. TODO check all units

Q10 computation

* stats

All data analysis and statistics were performed using R version 3.2.3 {R Development Core Team, 2016 #4314}. This experiment was run as an "open experiment" with all analysis code, data (raw to final), diagnostics, etc., available in real time at https://github.com/bpbond/cpcrw_incubation. The flux data backing the main results have also been archived at TODO.
